Papers

### 2023-02-09 quarto/index.qmd
update

* **A. Zhang**, M. Li, Z. C. Lipton, and A. J. Smola<br>
	<a href="https://zh.d2l.ai" target="_blank">动手学深度学习</a><br>
	*人民邮电出版社*, 2nd ed., 2023, 1st ed., 2019<br>
	* <a href="https://github.com/d2l-ai/d2l-zh/raw/v1/img/frontpage/jd-190715-en.png" target="_blank">Best seller</a> of new books in "Computers and Internet" at the largest Chinese online bookstore<br>
	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>

>>>>

* **A. Zhang**, M. Li, Z. C. Lipton, and A. J. Smola<br>
	<a href="https://zh.d2l.ai" target="_blank">动手学深度学习</a><br>
	*人民邮电出版社*, 2nd ed., 2023, 1st ed., 2019<br>
	* Best seller of new books in "Computers and Internet" at the largest Chinese online bookstore (both ed.)<br>
	<iframe src="https://ghbtns.com/github-btn.html?user=d2l-ai&repo=d2l-zh&type=star&count=true" frameborder="0" scrolling="0" width="150" height="30" title="GitHub"></iframe>
